Correlation

### 2022-03-16 graphs_newt_snakes/Comparing_GA_part_2.Rmd
working on fixing the correlation plots, and trying to figure out if there is a problem

title="Space: Newt VS Snake Boxplot Color=Mean_predation"
subt="25sims newt_deaths/Newt_pop_size last 100gen"
y_label="Mean_predation"
x_label="Simulation"
ggplot(GA_file[ which(GA_file$gen>4900),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation)), color="darkolivegreen4")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

@@

@@

Here I want to look at some boxplots of the phenotype and predation from the 100,000 generation simulation.

```{r, boxplottinh}
GA_file_100$mean_predation <- GA_file_100$newt_deaths/GA_file_100$Newt_pop_size

GA_file_100$gen_boxy <- round_any(GA_file_100$gen, 1000, f = ceiling) 
ggplot(data = GA_file_100[which(GA_file_100$gen_boxy>=95000),], aes(x = factor(gen_boxy), y = mean_predation)) +
  facet_wrap(~sim)+
  geom_boxplot() +
  xlab("Generation") +
  ylab("mean_predation")

>>>>

title="Space: Newt VS Snake Boxplot Color=Mean_predation"
subt="25sims newt_deaths/Newt_pop_size last 100gen"
y_label="Mean_predation"
x_label="Simulation"
ggplot(GA_file[ which(GA_file$gen>4900),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation)), color="darkolivegreen4")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
```

These figures show the predation level for the last 1000 and 100 generations on the y-axis. The x-axis has the simulations that I ran with different parameters. For every chunk of five letters the snakes GA stays the same while the newts GA decreases mutation rate and increases effect size. Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size. The first thing that I noticed is that there is more variation in predation in the 1000 gen figures than in the 100 gen figure. This is probably due to more generations being considered. I noticed that higher predation matches up to a higher phenotype, but not in all of the cases

```{r, boxplotting the phenotype}

@@

```
These figures show the mean newt phenotype, mean snake phenotype, and the difference between snake and newt mean phenotype (red, blue, and purple) for the last 1000 and 100 generations on the y-axis. The x-axis has the simulations that I ran with different parameters. For every chunk of five letters the snakes GA stays the same while the newts GA decreases mutation rate and increases effect size. Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size. I noticed that the newts have a higher phenotype in most of the simulations. I wonder if there is a connection between GA and species phenotype.

@@

```{r, boxplotting 100000}
title="Space: Newt VS Snake Boxplot Color=Mean_predation"
subt="25sims 100000gen newt_deaths/Newt_pop_size last 1000gen"
y_label="Mean_predation"
x_label="Simulation"

data_subset1 <- GA_file_100[which(GA_file_100$gen>4000 & GA_file_100$gen<=5000),]
data_subset1$group <- "A 5000"
data_subset2 <- GA_file_100[which(GA_file_100$gen>19000 & GA_file_100$gen<=20000),]
data_subset2$group <- "B 20000"
data_subset3 <- GA_file_100[which(GA_file_100$gen>99000),]
data_subset3$group <- "C 100000"

data_subset<-rbind(data_subset1, data_subset2, data_subset3)

ggplot(data_subset) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation), fill=group), color="black")+

  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

data_subset1 <- GA_file_100[which(GA_file_100$gen>4900 & GA_file_100$gen<=5000),]
data_subset1$group <- "A 5000"
data_subset2 <- GA_file_100[which(GA_file_100$gen>19900 & GA_file_100$gen<=20000),]
data_subset2$group <- "B 20000"
data_subset3 <- GA_file_100[which(GA_file_100$gen>99900),]
data_subset3$group <- "C 100000"

data_subset_small<-rbind(data_subset1, data_subset2, data_subset3)

title="Space: Newt VS Snake Boxplot Color=Mean_predation"
subt="25sims 100000gen newt_deaths/Newt_pop_size last 100gen"
y_label="Mean_predation"
x_label="Simulation"
ggplot(data_subset_small) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation), fill=group), color="black")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
```

These figures show the predation level for the last 1000 and 100 generations (for 5000, 20000, and 100000, generation within the same simulation) on the y-axis. The x-axis has the simulations that I ran with different parameters. For every chunk of five letters the snakes GA stays the same while the newts GA decreases mutation rate and increases effect size. Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size. These values seem to differ by simulation, F and H are specifically larger than the others. The predation figures match the phenotypes in the next figure set.

```{r, boxplotting the phenotype}

title="Space: Newt VS Snake Boxplot Phenotype"
subt="25sims dif last 1000gen"
y_label="dif"
x_label="Simulation"
ggplot(data_subset) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif), fill=group), color="darkorchid4")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno), fill=group), color="darkred")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

title="Space: Newt VS Snake Boxplot Phenotype"
subt="25sims dif last 100gen"
y_label="dif"
x_label="Simulation"
ggplot(data_subset_small) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif), fill=group), color="darkorchid4")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno), fill=group), color="darkred")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

```
These figures show the mean newt phenotype, mean snake phenotype, and the difference between snake and newt mean phenotype (red, blue, and purple) for the last 1000 and 100 generations on the y-axis. The x-axis has the simulations that I ran with different parameters with three groups (5000, 20,000, and 100,000). For every chunk of five letters the snakes GA stays the same while the newts GA decreases mutation rate and increases effect size. Every fifth letter the newts GA stays the same while the snakes GA decreases mutation rate and increases effect size. I see some larger flucations in the mean phenotype difference with in a simulations. There could be cycling

### 2022-03-16 graphs_newt_snakes/Correlation.Rmd
working on fixing the correlation plots, and trying to figure out if there is a problem

@@

@@

@@

@@

  GA_5000_file <- rbind(GA_5000_file, lit_temp_file)
  GA_20000_file <- rbind(GA_20000_file, lit_temp_file_2)
  GA_100000_file <- rbind(GA_100000_file, lit_temp_file_3)
  GA_5000_file_88 <- rbind(GA_5000_file_88, lit_temp_file_4)
  GA_5000_file_1010 <- rbind(GA_5000_file_1010, lit_temp_file_5)

  cor_5000_file <- rbind(cor_5000_file, cor_temp_file)
  cor_20000_file <- rbind(cor_20000_file, cor_temp_file_2)
  cor_100000_file <- rbind(cor_100000_file, cor_temp_file_3)
  cor_5000_file_88 <- rbind(cor_5000_file_88, cor_temp_file_4)
  cor_5000_file_1010 <- rbind(cor_5000_file_1010, cor_temp_file_5)

@@

GA_5000_file$dif <- GA_5000_file$Snake_mean_Pheno-GA_5000_file$Newt_mean_Pheno
GA_20000_file$dif <- GA_20000_file$Snake_mean_Pheno-GA_20000_file$Newt_mean_Pheno
GA_100000_file$dif <- GA_100000_file$Snake_mean_Pheno-GA_100000_file$Newt_mean_Pheno
GA_5000_file_88$dif <- GA_5000_file_88$Snake_mean_Pheno-GA_5000_file_88$Newt_mean_Pheno
GA_5000_file_1010$dif <- GA_5000_file_1010$Snake_mean_Pheno-GA_5000_file_1010$Newt_mean_Pheno
GA2_GA_5000_file$dif <- GA2_GA_5000_file$Snake_mean_Pheno-GA2_GA_5000_file$Newt_mean_Pheno
GA2_GA_5000_file$dif <- GA2_GA_5000_file$Snake_mean_Pheno-GA2_GA_5000_file$Newt_mean_Pheno
```

@@

>>>>

lit_5000_files_2020 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA2020_lit_", full.names=TRUE, recursive=FALSE)
cor_5000_files_2020 <- list.files(path="~/Desktop/cor_5000/text_files", pattern="GA2020_cor_", full.names=TRUE, recursive=FALSE)

@@

cor_5000_file_2020 <- read.table(cor_5000_files_2020[number], header = TRUE)
GA_5000_file_2020 <- read.table(lit_5000_files_2020[number], header = TRUE)

@@

GA_5000_file_2020$sim <-"A"
cor_5000_file_2020$sim <-"A"

@@

  lit_temp_file_6 <- read.table(lit_5000_files_2020[i], header = TRUE)
  lit_temp_file_6$sim <-LETTERS[i]

@@

  cor_temp_file_6 <- read.table(cor_5000_files_2020[i], header = TRUE)
  cor_temp_file_6$sim <-LETTERS[i]

  GA_5000_file <- rbind(GA_5000_file, lit_temp_file)
  GA_20000_file <- rbind(GA_20000_file, lit_temp_file_2)
  GA_100000_file <- rbind(GA_100000_file, lit_temp_file_3)
  GA_5000_file_88 <- rbind(GA_5000_file_88, lit_temp_file_4)
  GA_5000_file_1010 <- rbind(GA_5000_file_1010, lit_temp_file_5)
  GA_5000_file_2020 <- rbind(GA_5000_file_2020, lit_temp_file_6)

  cor_5000_file <- rbind(cor_5000_file, cor_temp_file)
  cor_20000_file <- rbind(cor_20000_file, cor_temp_file_2)
  cor_100000_file <- rbind(cor_100000_file, cor_temp_file_3)
  cor_5000_file_88 <- rbind(cor_5000_file_88, cor_temp_file_4)
  cor_5000_file_1010 <- rbind(cor_5000_file_1010, cor_temp_file_5)
  cor_5000_file_2020 <- rbind(cor_5000_file_2020, cor_temp_file_6)

@@

GA_5000_file$dif <- GA_5000_file$Snake_mean_Pheno-GA_5000_file$Newt_mean_Pheno
GA_20000_file$dif <- GA_20000_file$Snake_mean_Pheno-GA_20000_file$Newt_mean_Pheno
GA_100000_file$dif <- GA_100000_file$Snake_mean_Pheno-GA_100000_file$Newt_mean_Pheno
GA_5000_file_88$dif <- GA_5000_file_88$Snake_mean_Pheno-GA_5000_file_88$Newt_mean_Pheno
GA_5000_file_1010$dif <- GA_5000_file_1010$Snake_mean_Pheno-GA_5000_file_1010$Newt_mean_Pheno
GA_5000_file_2020$dif <- GA_5000_file_2020$Snake_mean_Pheno-GA_5000_file_2020$Newt_mean_Pheno
GA2_GA_5000_file$dif <- GA2_GA_5000_file$Snake_mean_Pheno-GA2_GA_5000_file$Newt_mean_Pheno
GA2_GA_5000_file$dif <- GA2_GA_5000_file$Snake_mean_Pheno-GA2_GA_5000_file$Newt_mean_Pheno
```

@@

```{r, correlation 5000 2020}

title="Space: Newt VS Snake"
subt="5,000 Gen Grid 20 by 20"
y_label="Generation"
x_label="Correlation"
cors_by_gen(cor_5000_file_2020, title, subt, x_label, y_label)

title="Phenotpe by Gen For all Sims"
subt="GA1 5,000 Gen"
y_label="Phenotype"
trends_by_gen(GA_5000_file_2020, title, subt, x_label, y_label)
